---
title: "ANIMO feasibility results"
author: "Kyle Humphrey"
date: "`r format(Sys.time(), '%B %e %Y')`"
output: html_document
params: 
  input_data: "default"
---

```{r setup, echo = F, message = F, warning = F}
knitr::opts_chunk$set(
  cache = T,
  cache.path = "../cache/feas/",
  autodep = T,
  echo = F,
  warning = F,
  message = F,
  fig.align = "center",
  root.dir = '..'
)
knitr::opts_knit$set(root.dir = '..')
pacman::p_load(tidyverse, Gmisc, glue)
```

```{r load data}
animo <- read_rds(params$input_data[1])
screen <- read_csv(params$input_data[2],
                   col_types = cols(.default = col_character())) %>%
  select(eligible_esf)
```



# Recruitment

```{r recruitment}
num_screened <- nrow(screen)
num_eligible <- sum(screen$eligible_esf == "1")
num_ineligible <- sum(screen$eligible_esf == "0")
num_enrolled <- animo %>% select(participant_id) %>% distinct() %>% nrow()
```

`r num_screened` were screened for eligibility, of these, `r num_eligible` were eligible, and `r num_ineligible` were ineligible for study inclusion. `r num_enrolled` participants enrolled in the trial. Since recruitment lasted approximately from June through August 2016, approximately `r round(num_enrolled/12, 1)` participants were enrolled per week, exceeding the target of 2.2 per week.

Two participants dropped out of the trial before randomization and were removed from all analyses.

```{r remove non-randomized}
animo <- animo %>% filter(!is.na(group))
```



# Retention

```{r retention}
weeks <- c(12, 24)
map(weeks,
    ~ animo %>%
      filter(week == .x) %>%
      summarise(retained = sum(!is.na(weight)),
                total = nrow(.))) %>%
  map_df(
    ~ Hmisc::binconf(x = .$retained, n = .$total) %>% signif(2) %>% as_tibble()
  ) %>%
  mutate(Week = weeks, `95% CI` = glue("({Lower}, {Upper})")) %>%
  select(Week, "Proportion retained" = PointEst, `95% CI`, -Lower, -Upper) %>%
  knitr::kable(align = "c")
```

A participant was classified as retained in the study at week 12 or 24 if a weight measurement was recorded for that week.



# Satisfaction

```{r satisfaction table setup}
satisfaction_labs <-
  tribble(
    ~ name,
    ~ label,
    'satisfied_tss',
    "How satisfied are you overall with the weight management program?",
    'rec_tss',
    "Would you recommend the weight management program you received to others?",
    'progress_why_tss',
    "Given the effort you put into following the weight management program, how satisfied are you with your overall progress over the past 12 weeks?",
    'chng_weight_tss',
    "Changing your weight",
    'chng_diet_tss',
    "Changing your dietary habits",
    'chng_pa_tss',
    "Changing your physical activity habits"
  )

satisfaction_labs <- satisfaction_labs %>% mutate(label = ifelse(
  name %in% c('chng_weight_tss', 'chng_diet_tss', 'chng_pa_tss'),
  paste(
    "Given the effort you put into following the weight management",
    "program for the past 12 weeks, how satisfied are you overall with your",
    "progress on...",
    label
  ),
  label
))
```

```{r make satisfaction tables, results="asis"}
weeks <- c(12, 24)
descrip_stats <- map(weeks, function(wk) {
  df <- filter(animo, week == wk)
  map(
    satisfaction_labs$name,
    ~ getDescriptionStatsBy(
      df[[.x]],
      df$group,
      continuous_fn = describeMedian,
      add_total_col = T
    ))
}) %>% set_names(paste0("week", weeks))

n.rgroups <- map(descrip_stats, ~ map_int(.x, nrow))

tables <- descrip_stats %>% map(reduce, rbind)

# remove WLC column which doesn't have data at week 12
tables$week12 <- tables$week12[ , "GCSWLI", drop = F]

captions <- c("Satisfaction at week 12", "Satisfaction at week 24")
pwalk(
  list(tables, n.rgroups, captions), ~
    htmlTable(
      ..1,
      rgroup = satisfaction_labs$label,
      n.rgroup = ..2,
      caption = ..3,
      tfoot = paste("Given the effort... questions were answered on a scale from",
                    "-4 (very dissatisfied) to 4 (very satisfied).")
    ) %>% print()
)
```

